### 2025-09-11 data-visualization.qmd
20250822 - clean up code
20250911 - geom_violin update to accommodate ggplot 4.0

The Okabe-Ito color palette [@Okabe2008] is depicted in Figures [-@fig-okabeItoPaletteGray] and [-@fig-okabeItoPaletteBlack].

@@

graphics::pie(rep(1, 8), col = palette_OkabeIto)
```

@@

graphics::pie(rep(1, 8), col = palette_OkabeIto_black)
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = fantasyPoints,
    fill = position_group)
) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) +
  labs(
    x = "Position",
    y = "Fantasy Points",
    title = "Violin Plot of Fantasy Points by Position",
    subtitle = "Lines represent the 25th, 50th, and 75th quantiles"
  ) +
  theme_classic() + 
  theme(
    legend.position = "none",
    axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

>>>>

The Okabe-Ito color palette [@Okabe2008] is depicted in Figures [-@fig-okabeItoPaletteGray] and [-@fig-okabeItoPaletteBlack].
You can see a pie chart of colors using the `graphics::pie()` function:

@@

pie(
  rep(1, 8),
  col = palette_OkabeIto)
```

@@

pie(
  rep(1, 8),
  col = palette_OkabeIto_black)
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = fantasyPoints,
    fill = position_group)
) +
  geom_violin(
    quantiles = c(0.25, 0.5, 0.75),
    quantile.linetype = "solid"
  ) +
  labs(
    x = "Position",
    y = "Fantasy Points",
    title = "Violin Plot of Fantasy Points by Position",
    subtitle = "Lines represent the 25th, 50th, and 75th quantiles"
  ) +
  theme_classic() + 
  theme(
    legend.position = "none",
    axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```
